Capital Budget Funding in Toronto

### 2024-09-26 paper/paper.qmd
highlighted important rows in the table

# Format numeric columns with conditional formatting for LaTeX
merged_table_2 <- merged_table_select |>
  mutate(
    # Format Per Capita Funding as dollars
    per_capita_funding = dollar(per_capita_funding),
      `Median total income of households in 2020 ($)` = paste0(
      dollar(as.numeric(`Median total income of households in 2020 ($)`)),
      ifelse(as.numeric(`Median total income of households in 2020 ($)`) <= 84000, "**", "")
    ),
    `Prevalence of low income based on the Low-income measure, after tax (LIM-AT) (%)` = paste0(round(as.numeric(`Prevalence of low income based on the Low-income measure, after tax (LIM-AT) (%)`) * 100, 2), "%"),
    `Bachelor’s degree or higher per capita` = paste0(round(as.numeric(`Bachelor’s degree or higher per capita`) * 100, 2), "%"),
    `Total visible minority population per capita` = paste0(round(as.numeric(`Total visible minority population per capita`) * 100, 2), "%")
  )

# Create the table with kable and apply enhanced styling
kable(
  merged_table_2, 
  escape = TRUE,                   
  col.names = c(
    "Ward Number", 
    "Per Capita Funding", 
    "Household Median Income", 
    "Low Income Prevalence", 
    "Bachelor’s Degree or Higher", 
    "Visible Minority Population"
  )
) |>
  kable_styling(
    bootstrap_options = c("condensed"),  
    full_width = FALSE,  
    position = "left",  
    font_size = 7 
  ) |>
  column_spec(1, width = "2cm") |>
  column_spec(2:3, width = "3cm") |>
  column_spec(4, width = "2cm") |>
  column_spec(5:6, width = "3cm")
```

>>>>

# Format numeric columns with conditional formatting for LaTeX
merged_table_2 <- merged_table_select |>
  mutate(
    # Format Per Capita Funding as dollars
    per_capita_funding = dollar(per_capita_funding),
    `Median total income of households in 2020 ($)` = paste0(dollar(as.numeric(`Median total income of households in 2020 ($)`))),
    `Prevalence of low income based on the Low-income measure, after tax (LIM-AT) (%)` = paste0(round(as.numeric(`Prevalence of low income based on the Low-income measure, after tax (LIM-AT) (%)`) * 100, 2), "%"),
    `Bachelor’s degree or higher per capita` = paste0(round(as.numeric(`Bachelor’s degree or higher per capita`) * 100, 2), "%"),
    `Total visible minority population per capita` = paste0(round(as.numeric(`Total visible minority population per capita`) * 100, 2), "%")
  )

# Create the table with kable and apply enhanced styling
kable(
  merged_table_2, 
  escape = TRUE,                   
  col.names = c(
    "Ward Number", 
    "Per Capita Funding", 
    "Household Median Income", 
    "Low Income Prevalence", 
    "Bachelor’s Degree or Higher", 
    "Visible Minority Population"
  )
) |>
  kable_styling(
    bootstrap_options = c("condensed"),  
    full_width = FALSE,  
    position = "left",  
    font_size = 7 
  ) |>
  add_footnote("Rows in red indicate a ward where the Household Median Income is $84,000 or less", notation="alphabet") |>
  column_spec(1, width = "2cm") |>
  column_spec(2:3, width = "3cm") |>
  column_spec(4, width = "2cm") |>
  column_spec(5:6, width = "3cm") |>
  row_spec(1, color = "red") |>
  row_spec(6, color = "red") |>
  row_spec(9:10, color = "red") |>
  row_spec(13:14, color = "red") |>
  row_spec(17:19, color = "red") |>
  row_spec(21:24, color = "red")
```
